parental migration and adolescents educational performance

### 2023-03-24 MScThesisText.Rmd
formatting

I adopted `R` (version 4.2.2) for all the analyses [@R-base]. This involved the following packages: `tidyverse` (version 2.0.0) and `haven` (version 2.5.0) for data cleaning [@R-tidyverse; @R-haven]; `fixest` (version 0.11.1) for econometric modeling [@R-fixest]; `MatchIt` (version 4.5.1) and `cobalt` (version 4.3.2) for matching [@ho2011; @R-MatchIt; @R-cobalt]; `modelsummary` (version 1.3.0), `vtable` (version 1.4.1), and `kableExtra` (version 1.3.4) for presenting the results [@R-modelsummary; @R-vtable; @R-kableExtra]; and `papaja` (version 0.1.1) for typesetting [@R-papaja].

>>>>

I adopted `R` (version 4.2.2) for all the analyses [@R-base]. This involved the following packages: `tidyverse` (version 2.0.0) and `haven` (version 2.5.2) for data cleaning [@R-tidyverse; @R-haven]; `fixest` (version 0.11.1) for econometric modeling [@R-fixest]; `MatchIt` (version 4.5.2) and `cobalt` (version 4.5.0) for matching [@ho2011; @R-MatchIt; @R-cobalt]; `modelsummary` (version 1.3.0), `vtable` (version 1.4.2), and `kableExtra` (version 1.3.4) for presenting the results [@R-modelsummary; @R-vtable; @R-kableExtra]; and `papaja` (version 0.1.1) for typesetting [@R-papaja].

### 2023-03-24 MScThesisText.tex
formatting

I adopted \texttt{R} (version 4.2.2) for all the analyses (R Core Team, 2022). This involved the following packages: \texttt{tidyverse} (version 2.0.0) and \texttt{haven} (version 2.5.0) for data cleaning (Wickham et al., 2019, 2023); \texttt{fixest} (version 0.11.1) for econometric modeling (Berge et al., 2023); \texttt{MatchIt} (version 4.5.1) and \texttt{cobalt} (version 4.3.2) for matching (Greifer, 2022; Ho et al., 2023, 2011); \texttt{modelsummary} (version 1.3.0), \texttt{vtable} (version 1.4.1), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2023; Zhu, 2021); and \texttt{papaja} (version 0.1.1) for typesetting (Aust \& Barth, 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-nbs2022}{}}%
NBS. (2022). \emph{2021 migrant workers monitor survey report {[}in Chinese{]}}. National Bureau of Statistics. \url{http://www.stats.gov.cn/tjsj/zxfb/202204/t20220429_1830126.html}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wang2015}{}}%
Wang, W., \& Li, P. (2015). \emph{Psychometric report for the cognitive ability tests of CEPS baseline survey (in chinese)}. \url{http://ceps.ruc.edu.cn/Enlish/dfiles/11184/14507142239451.pdf}

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-haven}{}}%
Wickham, H., Miller, E., \& Smith, D. (2023). \emph{Haven: Import and export 'SPSS', 'stata' and 'SAS' files}. \url{https://CRAN.R-project.org/package=haven}

>>>>

I adopted \texttt{R} (version 4.2.2) for all the analyses (R Core Team, 2022). This involved the following packages: \texttt{tidyverse} (version 2.0.0) and \texttt{haven} (version 2.5.2) for data cleaning (Wickham et al., 2019, 2023); \texttt{fixest} (version 0.11.1) for econometric modeling (Berge et al., 2023); \texttt{MatchIt} (version 4.5.2) and \texttt{cobalt} (version 4.5.0) for matching (Greifer, 2022; Ho et al., 2023, 2011); \texttt{modelsummary} (version 1.3.0), \texttt{vtable} (version 1.4.2), and \texttt{kableExtra} (version 1.3.4) for presenting the results (Arel-Bundock, 2022; Huntington-Klein, 2023; Zhu, 2021); and \texttt{papaja} (version 0.1.1) for typesetting (Aust \& Barth, 2022).

@@

\leavevmode\vadjust pre{\hypertarget{ref-nbs2022}{}}%
NBS. (2022). \emph{2021 migrant workers monitor survey report {[}in {Chinese}{]}}. National Bureau of Statistics. \url{http://www.stats.gov.cn/tjsj/zxfb/202204/t20220429_1830126.html}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wang2015}{}}%
Wang, W., \& Li, P. (2015). \emph{Psychometric report for the cognitive ability tests of {CEPS} baseline survey (in {Chinese})}. \url{http://ceps.ruc.edu.cn/Enlish/dfiles/11184/14507142239451.pdf}

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-haven}{}}%
Wickham, H., Miller, E., \& Smith, D. (2023). \emph{Haven: Import and export {SPSS}, {Stata} and {SAS} files}. \url{https://CRAN.R-project.org/package=haven}

### 2023-03-24 analysis/Gu-thesis-script.Rmd
formatting

## Matching
```{r Match on any parent migration}
m.out <- matchit(
  migr ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet, 
  data = df, 
  ratio = 3,
  method = "optimal", 
  distance = "glm",
  exact= migr ~ ctyids
  )
```

@@

```{r Match on mother-only migration}
d_mo_only <- d_cl |> drop_na(migr_mo_only)
m.out_mo_only <- 
  matchit(migr_mo_only ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet, 
  data = d_mo_only, 
  method = "optimal",
  distance = "glm",
  ratio = 3,
  exact= migr_mo_only ~ ctyids
  )
```

@@

```{r Match on father-only migration}
d_fa_only <- d_cl |> drop_na(migr_fa_only)
m.out_fa_only <- matchit(
  migr_fa_only ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet,
  data = d_fa_only,
  method = "optimal",
  distance = "glm",
  ratio = 3,
  exact= migr_fa_only ~ ctyids
  )
```

@@

```{r Match on both parents migration}
d_both <- d_cl |> drop_na(migr_both) 
m.out_both <- matchit(
  migr_both ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level +  home.economic.resource + home.extracurricular.book + home.has.internet, 
  data = d_both, 
  method = "optimal",
  distance = "glm",
  ratio = 3,
  exact= migr_both ~ ctyids
  )
```

>>>>

## Matching
```{r Match on any parent migration}
m.out <- matchit(
  migr ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet, 
  data = df, 
  ratio = 3,
  method = "optimal", 
  distance = "glm",
  exact = migr ~ ctyids
  )
```

@@

```{r Match on mother-only migration}
d_mo_only <- d_cl |> drop_na(migr_mo_only)
m.out_mo_only <- 
  matchit(migr_mo_only ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet, 
  data = d_mo_only, 
  method = "optimal",
  distance = "glm",
  ratio = 3,
  exact = migr_mo_only ~ ctyids
  )
```

@@

```{r Match on father-only migration}
d_fa_only <- d_cl |> drop_na(migr_fa_only)
m.out_fa_only <- matchit(
  migr_fa_only ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet,
  data = d_fa_only,
  method = "optimal",
  distance = "glm",
  ratio = 3,
  exact = migr_fa_only ~ ctyids
  )
```

@@

```{r Match on both parents migration}
d_both <- d_cl |> drop_na(migr_both) 
m.out_both <- matchit(
  migr_both ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level +  home.economic.resource + home.extracurricular.book + home.has.internet, 
  data = d_both, 
  method = "optimal",
  distance = "glm",
  ratio = 3,
  exact = migr_both ~ ctyids
  )
```
